Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
Remove note about not dealing with "rich" sharing

At first, for ease of exposition, our development assumes a single simple
stack with no sharing between callers and callees: all parameters and return
values are passed in registers.  Later, we show how to refine the properties
to allow passing of scalar stack data, granting a callee access to the
caller's data. (We do not consider more sophisticated forms of sharing, such
as taking the address of a variable and treating it like a pointer.)
\rb{But actually, this is discussed at some length is \cref{sec:passing},
  and it is the topic of \cref{fig:passing}.  Reaching that point after
  reading this disclaimer is confusing.}\bcp{So should we just remove that
  sentence?}
%
Lastly, we define integrity and confidentiality properties for a coroutine
system with a static layout, in which each coroutine's stack is constrained
to a fixed region of memory.  Though simplistic, this extension is a step
toward full-blown concurrency and demonstrates that our approach is flexible
enough to handle more sophisticated styles of control flow.

>>>>

At first, for ease of exposition, our development assumes a single simple
stack with no sharing between callers and callees: all parameters and return
values are passed in registers.  Later, we show how to refine the properties
to allow passing of scalar stack data, granting a callee access to the
caller's data.
%% (We do not consider more sophisticated forms of sharing, such
%% as taking the address of a variable and treating it like a pointer.)
%% \rb{But actually, this is discussed at some length is \cref{sec:passing},
%%   and it is the topic of \cref{fig:passing}.  Reaching that point after
%%   reading this disclaimer is confusing.}\bcp{So should we just remove that
%%   sentence?}
%
Lastly, we define integrity and confidentiality properties for a coroutine
system with a static layout, in which each coroutine's stack is constrained
to a fixed region of memory.  Though simplistic, this extension is a step
toward full-blown concurrency and demonstrates that our approach is flexible
enough to handle more sophisticated styles of control flow.
